`State and Parameter Estimation for Spatio-Temporal Neural Fields' or `A Data Driven Framework for Patient-Specific Neural Field Modelling'

### 2010-06-22 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
edits to appendices

\section{Calculation of Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}

@@

\section{Convolution of two $n$-dimensional Gaussian basis functions}\label{ap:ConvOfGaussians}

@@

\section{Inner Product Bit}\label{ap:InnerProdOfGaussians}

>>>>

\section{Spatial Cut-off Frequency of Field Basis Functions}\label{ap:FrequencyAnalysis}

@@

\section{Convolution of Two $n$-Dimensional Gaussians}\label{ap:ConvOfGaussians}

@@

\section{Inner Product of Two \emph{n}-Dimensional Gaussians}\label{ap:InnerProdOfGaussians}
